Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-05 ppdp24/hyper.tex
checkpoint

In this Section we formulate probabilistic versions of well-studied
hyperproperties of confidentiality and integrity, including noninterference,
gradual release, declassification, and robust declassification.
We demonstrate a soundness relation between noninterference and
passive security, and between robust declassification and malicious
security. We subsequently leverage this relation to enforce
malicious security using ``traditional'' security type methods
in Section \ref{section-types}. Previous work has explored
a similar approach to security type enforcement
\cite{6266151,almeida2018enforcing} but mainly
for aspects of passive security.

@@

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.  As
discussed in Section \ref{section-lang}, public reveals and protocol
outputs are fundamentally forms of declassification.  But consistent
with other work \cite{8429300}, we can formulate a version of
probabilistic noninterence conditioned on output that is sound
for passive security. It says that if two low-equivalent secret
inputs generate the same output, then the distributions of corrupt
views are the same. 
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ and 
  $\store_1,\store_2 \in \mems(S)$ we have:
  $$
  (\store_1 =_C \store_2 \ \wedge \ 
  (\condd{\progtt(\prog)}{O}{\store_1} = \condd{\progtt(\prog)}{O}{\store_2}))
  \implies 
  (\condd{\progtt(\prog)}{\houtputs}{\store_1} = \condd{\progtt(\prog)}{\houtputs}{\store_2})
  $$
  where $\iov(\prog) = S \cup V \cup O$.
\end{definition}
Intuitively, this conditional noninterference property implies that
the simulator can just run the protocol in simulation to
reconstruct real world corrupt view distributions. But it requires
that the simulator can tractably ``pre-image'' a given output of
a functionality $\idealf$, to determine the inputs that
could have produced it. This pre-image is called a
\emph{kernel} in recent work \cite{XXX}.
\begin{definition}
  Given a functionality $\idealf$ and output value $v$, its
  \emph{kernel}, denoted $\ik(\idealf,v)$ is
  $
  \{ \store\ |\ \idealf(\store) = v \}
  $.
  We say that $\idealf$ is \emph{pre-imageable} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
A soundness result for passive security can then be given as follows.
It is essentially the same as ``perfect passive NI security'' explored
in previous work \cite{8429300}.  
\begin{restatable}{theorem}{nimosecure}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\prog$ satisfies noninference modulo output
  then $\prog$ is passive secure.
\end{restatable}

\begin{proof}
  Let $H$ and $C$ be an arbitrary partition of the federation and
  suppose $\prog$ satisfies noninterference modulo output. Let
  $\iov(\prog) = (V,S)$ and $\flips(\prog) = F$ with output view $\outv
  \in V$ and let $\store$ be an arbitrary element of $\mems(S \cup
  F)$. Then the distribution of adversarial views in the real world
  is, by definition,
  $\condd{\progd(\prog)}{V_C}{\store_S}$.

  The simulator is given both $\store_{S_C}$ and
  $\idealf(\store_S)$.  The simulation $\SIM_C(\store_{S_C},
  \idealf(\store_S))$ can be defined as follows. First, some $\store'
  \in \ik(\idealf,\idealf(\store))$ is randomly chosen such that
  $\store' =_C \store_S$, as is a random tape $\store'' \in
  \mems(F)$\footnote{The real/ideal model allows consultation of a
  ``Random Oracle''.}. Then, the run of $(\store' \cup \store'',
  \prog)$ is evaluated in simulation, yielding $(\store^{\SIM},\varnothing)$.
  The simulation returns $\store^{\SIM}_{V_C}$ as a result.

  Now, since the random tape is selected in simulation from the same distribution
  that we assume for the real world, after selection of $\store'$ the
  probability that any particular $\store^{\SIM}_{V_C}$ is returned is by definition
  $
  \progd(\prog)(\store^{\SIM}_{V_C} | \store')
  $.
  Furthermore, since we assume that $\prog$ correctly implements $\idealf$, this
  means
  $
  \store_S =_C \store' \wedge
     \condd{\progd(\prog)}{\{ \outv \}}{\store_S} =
     \condd{\progd(\prog)}{\{ \outv \}}{\store'}
  $,
  so by the definition of noninterference modulo output,
  any choice of $\store'$ yields the same distribution $\condd{\progd(\prog)}{V_C}{\store_S}$.
  Therefore by definition
  $
   \progd(\SIM_C(\store_{S_C},\idealf(\store))) = \condd{\progd(\prog)}{V_C}{\store_S}
  $.
\end{proof}

@@

In fact, MPC protocols typically satisfy a \emph{delimited release}
property\cite{XXX}, where messages exchanged remain probabilistically separable
from secrets, with only declassification events (reveals and outputs)
releasing information about honest secrets. A key difference is that while
these declassification events essentially define the policy in delimited
release, the ideal functionality sets the release policy for MPC
passive security, so its necessary to show that declassification events respect
these bounds.
\begin{definition}
  Given $H,C$, a protocol $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  satisfies \emph{delimited release} iff
  $\sep{\progtt(\prog)}{M_C}{S_H}$.
\end{definition}

>>>>

In this Section we formulate probabilistic versions of well-studied
hyperproperties of confidentiality and integrity, including
noninterference, gradual release, declassification, and robust
declassification.  We follow nomenclature developed in previous work
on characterizing declassification policies in deterministic settings
\cite{sabelfeld2009declassification}, but adapt them to our
probabilistic one.

%We demonstrate a soundness relation between noninterference and
%passive security, and between robust declassification and malicious
%security.
%Some previous work on security type enforcement
%\cite{6266151,almeida2018enforcing} and has considered similar relationships
%but mainly for aspects of passive security.

@@

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.  As
discussed in Section \ref{section-lang}, public reveals and protocol
outputs are fundamentally forms of declassification.  But consistent
with other work \cite{8429300}, we can formulate a version of
probabilistic noninterence conditioned on output that is sound
for passive security. It says that if two low-equivalent secret
inputs generate the same output, then the distributions of corrupt
views are the same. 
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ with $\iov(\prog) = S \cup V \cup O$
  satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ and $\store_1 \in \mems(S_C \cup O)$ and $\store_2 \in \mems(\houtputs)$
  we have:
  $$
  \condd{\progtt(\prog)}{S_H}{\store_1} = \condd{\progtt(\prog)}{S_H}{\store_1 \cap \store_2}
 $$
\end{definition}
%\begin{definition}[Noninterference modulo output]
%  \label{definition-NIMO}
%  We say that a program $\prog$ satisfies \emph{noninterference modulo output}
%  iff for all $H$ and $C$ and 
%  $\store_1,\store_2 \in \mems(S)$ we have:
%  $$
%  (\store_1 =_C \store_2 \ \wedge \ 
%  (\condd{\progtt(\prog)}{O}{\store_1} = \condd{\progtt(\prog)}{O}{\store_2}))
%  \implies 
%  (\condd{\progtt(\prog)}{\houtputs}{\store_1} = \condd{\progtt(\prog)}{\houtputs}{\store_2})
%  $$
%  where $\iov(\prog) = S \cup V \cup O$.
%\end{definition}
Intuitively, this conditional noninterference property implies that
corrupt views give the adversary no better chance of guessing honest
secrets than the output and corrupt inputs do. So
the simulator can just arbitrarily pick any honest secrets that
produce the expected output and run the protocol in simulation to
reconstruct real world corrupt view distributions. But it requires
that the simulator can tractably ``pre-image'' a given output of
a functionality $\idealf$, to determine the inputs that
could have produced it. This pre-image is called a
\emph{kernel} in recent work \cite{XXX}.
\begin{definition}
  Given a functionality $\idealf$ and output value $v$, its
  \emph{kernel}, denoted $\ik(\idealf,v)$ is
  $
  \{ \store\ |\ \idealf(\store) = v \}
  $.
  We say that $\idealf$ is \emph{pre-imageable} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
A soundness result for passive security can then be given as follows.
It is essentially the same as ``perfect passive NI security'' explored
in previous work \cite{8429300}.  
\begin{restatable}{theorem}{nimosecure}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\prog$ satisfies noninference modulo output
  then $\prog$ is passive secure.
\end{restatable}

@@

In fact, MPC protocols typically satisfy a \emph{delimited release}
property\cite{sabelfeld2009declassification}, where messages exchanged remain probabilistically separable
from secrets, with only declassification events (reveals and outputs)
releasing information about honest secrets. A key difference is that while
these declassification events essentially define the policy in delimited
release, the ideal functionality sets the release policy for MPC
passive security, so its necessary to show that declassification events respect
these bounds.
\begin{definition}
  Given $H,C$, a protocol $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$
  satisfies \emph{delimited release} iff
  $\sep{\progtt(\prog)}{M_C}{S_H}$.
\end{definition}
